\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}
\namesection{Mithun}{Srinivasan}{ \urlstyle{same}\href{https://www.linkedin.com/in/mithun-srinivasan-msec/}{Linkedin} | \href{https://github.com/mithun-srinivasan}{Github} \\
\href{mailto:omsaimithun@gmail.com}{omsaimithun@gmail.com} | +91 9342099436
}


\begin{minipage}[t]{0.33\textwidth} 



\section{Education} 

\subsection{Meenakshi Sundararajan \\ Engineering College}
\descript{BE in Computer Science and Engineering}
\location{Jul 2025 - 2029 | Chennai, India}
\sectionsep

\subsection{Indian Institute  \\ of Technology \\ Madras}
\descript{BS in Data Science and Applications}
\location{May 2025 | Foundation Level |\\Online}
\location{CGPA: 6.0}
\sectionsep

\subsection{The Holy Cross \\ Matriculation \\Hr Sec School}
\descript{Class 12}
\location{Apr 2025 | Chennai, India}
\sectionsep



\section{Links} 
Github: \href{https://github.com/mithun-srinivasan}{\bf mithun-srinivasan} \\
LinkedIn: \href{https://www.linkedin.com/in/mithun-srinivasan-msec/}{\bf Mithun Srinivasan} \\
Instagram: \href{https://www.instagram.com/its_mithunsrinivasan/}{\bf its\_mithunsrinivasan} \\



\section{Skills}
\subsection{Programming}
\location{Over 200 lines:}
\textbullet{} C

\location{Familiar:}
\textbullet{} MATLAB
\textbullet{} Java
\textbullet{} C++

\sectionsep



\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 



\section{Experience}
\runsubsection{Member}
\descript{Sundarbans House IITM BS Degree}
\location{Sep 2025 - Present | Chennai, India}
\sectionsep





\section{Projects}
\runsubsection{Meeting Transcriber and Summarizer}
\descript{Developer}
\textbullet{} Engineered an AI-powered transcription and summarization tool using Python and cloud-based APIs, reducing the time spent searching for key information in meetings by 25\% for users.

\textbullet{} Integrated large language model APIs and on-device processing options to ensure data privacy and security.

\textbullet{} Designed the system to save time, boost productivity, and simplify meeting information retrieval for users.


I made this on my first hackathon with the help of my seniors.

\textbf{\href{https://github.com/mithun-srinivasan/meeting-transcriber-and-summarizer}{Github Link.}}
\sectionsep



\section{Languages}
\begin{tabular}{rll}
English& Limited working proficiency& \\
Hindi& Elementary proficiency& \\
Tamil& Native or bilingual proficiency& \\
Sanskrit& Elementary proficiency& \\
\end{tabular}
\sectionsep
\section{Certifications}

\runsubsection{MATLAB Onramp}
\begin{itemize}
    \item Learnt the basics of MATLAB.
\end{itemize}

\runsubsection{Wells Fargo – Personal Banker Job Simulation}
\begin{itemize}
    \item Completed on Forage
    \item Learned how to understand customer needs and suggest the right banking solutions.
    \item Practiced teamwork and communication in real-world situations.Improved my problem-solving skills while handling multiple tasks. 
\end{itemize}
\runsubsection{Goldman Sachs – Controllers Job Simulation}
\begin{itemize}
    \item Completed on Forage
    \item Learned the basics of financial analysis and reporting
    \item Used Excel for data checking, analysis, and reconciliation 
\end{itemize}

\end{minipage} 
\end{document}  \documentclass[]{article}
